Modified Silver Ion Chroma

### 2022-03-24 archive/isotope_data_reduction.rmd
move to archive folder

'
FL = 0.005 # tracer strength = 0.5% --> 
a = 0.5 # incorporation efficiency of 50%
FT = 0.02 # resultant isotopic enrichment
F0 = 0.0124 # beginning isotopic enrichment
'

>>>>

'
FL = 0.005 # tracer strength = 0.5% --> 
a = 0.5 # incorporation efficiency of 50%
FT = 0.02 # resulting isotopic enrichment
F0 = 0.0124 # beginning isotopic enrichment
'

### 2022-03-24 archive/modified_silver_ion_chroma.Rmd
move to archive folder

p_tc_bames2 <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = saturation, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~sample_f, ncol = 1, scales = "free_y") +
  ggtitle("BAMES Standard 10µg/µL") +
  theme_bw()

@@

```{results <- results %>%}
  group_by(sample) %>% 
  mutate(
    PAIBE_height = # PAIBE relative height value for given `sample`,
    rel_to_PAIBE = `Relative Height` * / PAIBE_height
    conc_ng_ul = rel_to_PAIBE * 10
  )

>>>>

plot_results <- plot_results %>% 
  mutate(fraction_eluent = case_when(
    sample == "tcbames3" ~ "NA",
    sample == "BAME_modagion_F1" ~ "F1 Hexane",
    sample == "BAME_modagion_F2" ~ "F2 99:1 Hex:ac",
    sample == "BAME_modagion_F3" ~ "F3 96:4 Hex:ac",
    sample == "BAME_modagion_F4" ~ "F4 90:10 Hex:ac",
    sample == "BAME_modagion_F5" ~ "F5 Acetone"
     )
  )

factored_eluents <- c('NA', 'F1 Hexane','F2 99:1 Hex:ac','F3 96:4 Hex:ac','F4 90:10 Hex:ac', 'F5 Acetone')
plot_results$fraction_eluent_f = factor(plot_results$fraction_eluent, levels=factored_eluents)

p_tc_bames2 <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = saturation, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
  ggtitle("BAMES Standard 10ng/µL") +
  theme_bw()

ggsave(filename = "fig_output/p_tc_bames2.png", plot = p_tc_bames2, height = 10, width = 7)

@@

    results <- results %>%
      group_by(sample) %>% 
      mutate(
        PAIBE_height = # PAIBE relative height value for given `sample`,
        rel_to_PAIBE = `Relative Height` * / PAIBE_height
        conc_ng_ul = rel_to_PAIBE * 10
      )

### 2022-03-24 archive/modified_silver_ion_chroma_2.Rmd
move to archive folder

Most compounds derivatized from the free fatty acid fraction (F4) of Jamie's Boulder soil sample are saturated FAMEs or not readily identifiable by mass spec. For clarity, sterols, alkanes, and ethers were excluded from the chromeleon data export. FAMEs are saturated unless noted otherwise.

```{r, fig.width=8, fig.height=10, warning=FALSE}
# Any necessary limitations to plotted results would go here
plot_results <- results

@@

p_sfames <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
  ggtitle("Boulder Soil Free FA as FAMES") +
  theme_bw()

p_sfames %>% ggplotly(dynamicTicks = TRUE, tooltip = c("key", "x", "y"))
```

>>>>

```{r, fig.width=8, fig.height=13, warning=FALSE}
# Any necessary limitations to plotted results would go here
plot_results <- results

@@

p_sfames <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`, label = saturation) +
  geom_bar(stat = 'identity', width = 0.1) +
  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
  ggtitle("Boulder Soil Free FA as FAMES") +
  geom_label_repel(data = subset(plot_results, saturation %in% c("n1 cis", "n1 trans")),
                   aes(vjust =-7, box.padding = 0.5),
                   show.legend = FALSE,
                   size = 2,
                   segment.alpha = 0.5) +
  theme_bw() +
  theme(legend.position = "bottom")

p_sfames
p_sfames %>% ggplotly(dynamicTicks = TRUE, tooltip = c("key", "x", "y"))
```
